\clearpage
\phantomsection
\addcontentsline{toc}{chapter}{Ном зүй}

\begin{thebibliography}{99}

\bibitem{bis2022}
Bank for International Settlements. (2022). \textit{Triennial Central Bank Survey of Foreign Exchange and Over-the-counter (OTC) Derivatives Markets in 2022}. BIS. [Online]. Available: https://www.bis.org/statistics/rpfx22.htm

\bibitem{barber2014}
Barber, B. M., Lee, Y. T., Liu, Y. J., \& Odean, T. (2014). The Cross-Section of Speculator Skill: Evidence from Day Trading. \textit{Journal of Financial Markets}, 18, 1-24.

\bibitem{mitchell1997}
Mitchell, T. M. (1997). \textit{Machine Learning}. New York: McGraw-Hill.

\bibitem{dietterich2000}
Dietterich, T. G. (2000). Ensemble Methods in Machine Learning. \textit{First International Workshop on Multiple Classifier Systems}, 1-15. Springer, Berlin, Heidelberg.

\bibitem{breiman2001}
Breiman, L. (2001). Random Forests. \textit{Machine Learning}, 45(1), 5-32.

\bibitem{chen2016}
Chen, T., \& Guestrin, C. (2016). XGBoost: A Scalable Tree Boosting System. \textit{Proceedings of the 22nd ACM SIGKDD International Conference on Knowledge Discovery and Data Mining}, 785-794.

\bibitem{ke2017}
Ke, G., Meng, Q., Finley, T., Wang, T., Chen, W., Ma, W., ... \& Liu, T. Y. (2017). LightGBM: A Highly Efficient Gradient Boosting Decision Tree. \textit{Advances in Neural Information Processing Systems}, 30.

\bibitem{murphy1999}
Murphy, J. J. (1999). \textit{Technical Analysis of the Financial Markets: A Comprehensive Guide to Trading Methods and Applications}. New York Institute of Finance.

\bibitem{krollner2010}
Krollner, B., Vanstone, B., \& Finnie, G. (2010). Financial Time Series Forecasting with Machine Learning Techniques: A Survey. \textit{European Symposium on Artificial Neural Networks}, 25-30.

\bibitem{fischer2018}
Fischer, T., \& Krauss, C. (2018). Deep Learning with Long Short-Term Memory Networks for Financial Market Predictions. \textit{European Journal of Operational Research}, 270(2), 654-669.

\bibitem{sezer2020}
Sezer, O. B., Gudelek, M. U., \& Ozbayoglu, A. M. (2020). Financial Time Series Forecasting with Deep Learning: A Systematic Literature Review: 2005–2019. \textit{Applied Soft Computing}, 90, 106181.

\bibitem{kim2018}
Kim, H. Y., \& Won, C. H. (2018). Forecasting the Volatility of Stock Price Index: A Hybrid Model Integrating LSTM with Multiple GARCH-Type Models. \textit{Expert Systems with Applications}, 103, 25-37.

\bibitem{ding2020}
Ding, Q., Wu, S., Sun, H., Guo, J., \& Guo, J. (2020). Hierarchical Multi-Scale Gaussian Transformer for Stock Movement Prediction. \textit{Proceedings of the 29th International Joint Conference on Artificial Intelligence (IJCAI)}, 4640-4646.

\bibitem{hochreiter1997}
Hochreiter, S., \& Schmidhuber, J. (1997). Long Short-Term Memory. \textit{Neural Computation}, 9(8), 1735-1780.

\bibitem{vaswani2017}
Vaswani, A., Shazeer, N., Parmar, N., Uszkoreit, J., Jones, L., Gomez, A. N., ... \& Polosukhin, I. (2017). Attention Is All You Need. \textit{Advances in Neural Information Processing Systems}, 30.

\bibitem{he2016}
He, K., Zhang, X., Ren, S., \& Sun, J. (2016). Deep Residual Learning for Image Recognition. \textit{Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition (CVPR)}, 770-778.

\bibitem{lin2017}
Lin, T. Y., Goyal, P., Girshick, R., He, K., \& Dollár, P. (2017). Focal Loss for Dense Object Detection. \textit{Proceedings of the IEEE International Conference on Computer Vision (ICCV)}, 2980-2988.

\bibitem{izmailov2018}
Izmailov, P., Podoprikhin, D., Garipov, T., Vetrov, D., \& Wilson, A. G. (2018). Averaging Weights Leads to Wider Optima and Better Generalization. \textit{Proceedings of the 34th Conference on Uncertainty in Artificial Intelligence (UAI)}, 876-885.

\bibitem{zhang2017}
Zhang, H., Cisse, M., Dauphin, Y. N., \& Lopez-Paz, D. (2017). mixup: Beyond Empirical Risk Minimization. \textit{arXiv preprint arXiv:1710.09412}.

\bibitem{wilder1978}
Wilder Jr, J. W. (1978). \textit{New Concepts in Technical Trading Systems}. Trend Research.

\bibitem{bollinger2002}
Bollinger, J. (2002). \textit{Bollinger on Bollinger Bands}. McGraw-Hill.

\bibitem{pytorch}
Paszke, A., Gross, S., Massa, F., Lerer, A., Bradbury, J., Chanan, G., ... \& Chintala, S. (2019). PyTorch: An Imperative Style, High-Performance Deep Learning Library. \textit{Advances in Neural Information Processing Systems}, 32.

\bibitem{reactnative}
Meta Platforms Inc. (2024). React Native: A Framework for Building Native Apps Using React. [Online]. Available: https://reactnative.dev/

\bibitem{metatrader}
MetaQuotes Software Corp. (2024). MetaTrader 5 Trading Platform. [Online]. Available: https://www.metatrader5.com/

\bibitem{scikit}
Pedregosa, F., Varoquaux, G., Gramfort, A., Michel, V., Thirion, B., Grisel, O., ... \& Duchesnay, É. (2011). Scikit-Learn: Machine Learning in Python. \textit{Journal of Machine Learning Research}, 12, 2825-2830.

\bibitem{kingma2014}
Kingma, D. P., \& Ba, J. (2014). Adam: A Method for Stochastic Optimization. \textit{arXiv preprint arXiv:1412.6980}.

\bibitem{loshchilov2017}
Loshchilov, I., \& Hutter, F. (2017). Decoupled Weight Decay Regularization. \textit{arXiv preprint arXiv:1711.05101}.

\bibitem{srivastava2014}
Srivastava, N., Hinton, G., Krizhevsky, A., Sutskever, I., \& Salakhutdinov, R. (2014). Dropout: A Simple Way to Prevent Neural Networks from Overfitting. \textit{Journal of Machine Learning Research}, 15(1), 1929-1958.

\bibitem{hu2018}
Hu, J., Shen, L., \& Sun, G. (2018). Squeeze-and-Excitation Networks. \textit{Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition (CVPR)}, 7132-7141.

\bibitem{graves2005}
Graves, A., \& Schmidhuber, J. (2005). Framewise Phoneme Classification with Bidirectional LSTM and Other Neural Network Architectures. \textit{Neural Networks}, 18(5-6), 602-610.

\end{thebibliography}
